\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2018-03-19 redaction/dhp_july2017.tex
Changer les graphiques Hummels

\begin{figure}[htbp]
\caption{Characterizing the time trends: Applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (a) Ad-valorem Air Freight} & {\small (b) Ad-valorem Vessel Freight}\\
\includegraphics[width=3in, height=2.5in]{figure5_comme_hummels.pdf}
& \includegraphics[width=3in,height=2.5in]{figure6_comme_hummels.pdf} \\
\includegraphics[width=3in, height=2.5in]{figure5_comme_hummels_base100.pdf}
& \includegraphics[width=3in,height=2.5in]{figure6_comme_hummels_base100.pdf} \\

@@

>>>>

\begin{figure}[htbp]
\caption{Characterizing the time trends: Applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
{\small (a) Ad-valorem Air Freight} & {\small (b) Ad-valorem Vessel Freight}\\
\includegraphics[width=3in, height=2.5in]{figure5_comme_hummels.pdf}
& \includegraphics[width=3in,height=2.5in]{figure6_comme_hummels.pdf} \\

@@

\begin{figure}[htbp]
\caption{Composition effect : comparing Hummels with our best guess}
\label{fig:comparingHummels_pond}
\begin{center}
\includegraphics[height=8cm]
{graph_comp_trend_hum_nous_.pdf}
\end{center}
\end{figure}

\begin{figure}[htbp]
\caption{Composition effect : comparing Hummels with our results with his weighting scheme}
\label{fig:comparingHummels_np}
\begin{center}
\includegraphics[height=8cm]
{graph_comp_trend_hum_nous__np.pdf}
\end{center}
\end{figure}
